Low-lying collective excited states in non-integrable pairing models based on stationary-phase approximation to path integral

### 2018-11-06 paper2/draft1-5.tex
revised draft1.5

For multi-level pairing models in Sec.~\ref{sec3}, 
there is a constant of motion in the TDHFB dynamics,
namely the average particle number $q^n\equiv \langle N \rangle/2$.
Since the particle number $N$ is time-even Hermitian operator, we treat
this as a coordinate, and its conjugate gauge angle, $p_n$,
as a momentum.
Since $q^n$ is a constant of motion, the Hamiltonian does not
depend on $p_n$.
On the other hand, the gauge angle $p_n$ changes in time,
which corresponds to the pair rotation, a Nambu-Goldstone (NG) mode
associated with the breaking of the gauge (particle-number) symmetry.
We assume the existence of 2D collective subspace $\Sigma_2$
(4D phase space),
described by a set of canonical variable $(q^1,q^2=q^n;p_1,p_2=p_n)$,
which is well decoupled from the rest of degrees of freedom,
$\{q^a,p_a\}$ with $a=3,\cdots$.
The collective Hamiltonian is given by imposing $q^a=p_a=0$,
namely by restricting the space into the collective subspace
\begin{equation}
%\mathcal{H}_{\rm coll}(q,p) &= \bar{V}(q) + \frac{1}{2}\bar{B}^{-1}(q)p^2 .
\mathcal{H}_{\rm coll}(q,p;q^n)
= \bar{V}(q^1,q^n) + \frac{1}{2}\bar{B}^{11}(q^1,q^n)p_1^2 .
  \label{coll}
\end{equation}
Since there exist two conserved quantities, $q^n$ and $\mathcal{H}_{\rm coll}$,
this 2D system is integrable.
We can treat the collective motion of $(q^1,p_1)$ separately from
the pair rotation $(q^n, p_n)$.

In the collective Hamiltonian (\ref{coll}), the variable $q^n$ is
trivially given as the particle number, which is expanded up to
second order in the momenta $\pi$,
\begin{equation}
q^n=\frac{\langle N \rangle}{2} = f^n(\xi)
	+\frac{1}{2}f^{(1)n\alpha\beta}\pi_\alpha\pi_\beta .
	\label{q^n}
\end{equation}
To obtain the non-trivial collective variables
$(q^1,p_1)$, we assume the point transformation\footnote{
We may lift the restriction to the point transformation,
as Eq. (\ref{q^n}) \cite{Sat18}.
In this paper, we neglect these higher-order terms, such as
$f^{(1)1\alpha\beta}\pi_\alpha\pi_\beta/2$.
},
\begin{equation}
%  q = q^1 &= f^1(\xi) + \frac{1}{2}f^{(1)1\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}  \label{point}\\
  q^1 = f^1(\xi) \label{point} ,
% \xi^{\alpha} &= g^{\alpha}(q) + \frac{1}{2}g^{(1)\alpha 1 1}(\xi)p_{1}p_{1}
\end{equation}
and $\xi^\alpha$ on the subspace $\Sigma_2$ is given as
$\xi^{\alpha} = g^{\alpha}(q^1,q^n,q^a=0)$.
The momenta on $\Sigma_2$ are transformed as
\begin{align}
p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha,
	\label{coll_momenta}\\
\pi_{\alpha} &= f^1_{,\alpha}p_1 +f^n_{,\alpha}p_n,
 \label{momenta}
\end{align}
where the comma indicates the partial derivative
$(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$. 
The Einstein's convention for summation with respect to the repeated
upper and lower indices is assumed hereafter.
The canonical variable condition leads to
\begin{align}
 %f^1_{,\alpha}g_{,1}^{\beta} = \delta^{\beta}_{\alpha}, \quad 
f^i_{,\alpha}g_{,j}^{\alpha} = \delta^i_j,
  \label{canonicity}
\end{align}
where $i,j=1$ and $n$.
The collective potential $\bar{V}(q^1,q^n)$ and
the collective mass parameter
$\bar{B}_{11}(q^1,q^n)=[\bar{B}^{11}(q^1,q^n)]^{-1}$ can be given by
\begin{align}
\bar{V}(q^1,q^n) &= V(\xi=g(q^1,q^n,q^a=0)), \\
\bar{B}^{11}(q^1,q^n) &= f^1_{,\alpha}\tilde{B}^{\alpha\beta}(\xi)f^1_{,\beta} ,
  \label{coll_mass}
\end{align}
where $\tilde{B}^{\alpha\beta}$ are defined as
\begin{align}
 \tilde{B}^{\alpha\beta}(\xi)
%&= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
&= B^{\alpha\beta}(\xi) - \bar{V}_{,n} f^{(1)n\alpha\beta}(\xi)
%- \lambda_1 f^{(1)1\alpha\beta}(\xi) 
\label{tildeB}.
\end{align}

@@

At each point in the space $(q^1,q^n; p_1,p_n)$ corresponds to
a generalized Slater determinant
$\ket{q^1,q^n;p_1,p_n}=\ket{\xi,\pi}$
where $(\xi,\pi)$ are given as
$\xi^\alpha=g^\alpha(q^1,q^n,q^a=0)$ and
$\pi_\alpha=f^1_{,\alpha}p_1+f^n_{,\alpha}p_n$.
According to the SPA, the $k$-th excited state $\ket{\psi_k}$
is constructed from the $k$-th periodic trajectory $C_k$,
given by $(q^1(t),p_1(t))$,
of the Hamiltonian $\mathcal{H}_{\rm coll}$.
\begin{equation}
%\ket{\psi_k} = \oint_{C_k} d\mu(q,p) \ket{q,p}
\ket{\psi_k} = \oint dp_n \oint_{C_k} \rho(q,p) dt \ket{q,p}
	e^{i\mathcal{T}[q,p]} ,
	\label{SPA}
\end{equation}
where $(q,p)$ means $(q^1,q^n;p_1, p_n)$, and the weight function
$\rho(q,p)$ is given through an invariant measure $d\mu(q,p)$ as
\begin{equation}
d\mu(q,p)=\rho(q,p) dE dt dq^n dp_n .
\end{equation}
The invariant measure $d\mu(q,p)$ is defined by the unity condition
$\int d\mu(q,p) \ket{q,p}\bra{q,p} = 1$.
An explicit form of $d\mu(q,p)$ for the present pairing model is shown
in Eq. (\ref{dmu}).
The action integral $\mathcal{T}$ is defined by
\begin{align}
\mathcal{T}[q,p] &\equiv
\int_{0}^{t} \braket{q(t'),p(t')| i\hbar\frac{\partial}{\partial t'}
	|q(t'),p(t')} dt' .
\label{tau}
\end{align}

@@

We study the low-lying excited $0^+$ states
in the multi-level pairing model by applying the ASCC+SPA.
The Hamiltonian of the pairing model is given in terms of
the single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{align}
	H &= \sum_\alpha \epsilon_\alpha n_\alpha - g \sum_{\alpha,\beta} S_\alpha^+ S_{\beta}^- \nonumber \\
    &= \sum_\alpha\epsilon_\alpha(2S_\alpha^0+\Omega_\alpha) - g S^+ S^{-} ,
\end{align}
where we use the SU(2) quasi-spin operators,
$\boldsymbol{S}=\sum_\alpha \boldsymbol{S}_\alpha$, with
\begin{eqnarray}
        S_\alpha^0 &=& \frac{1}{2}\left(\sum_ma_{j_\alpha m}^{\dag}a_{j_\alpha m}-\Omega_\alpha\right) ,\\
        S_\alpha^{+} &=& \sum_{m>0}a_{j_\alpha m}^{\dag}a_{j_\alpha\overline{m}}^{\dag} ,
\quad   S_\alpha^{-} = S_\alpha^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_\alpha$ possesses $2\Omega_\alpha$-fold
degeneracy ($\Omega_\alpha=j_\alpha+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$
and $\Omega_\alpha-1/2$.
The occupation number of each level $\alpha$ is given by
$n_\alpha = \sum_m a^{\dag}_{j_\alpha m}a_{j_\alpha m}
=2S_\alpha^0+\Omega_\alpha
$.
The quasi-spin operators satisfy the commutation relations
\begin{equation}
  [S_\alpha^0,S_\beta^{\pm}] = \pm\delta_{\alpha\beta}S_{\alpha}^{\pm},
\quad [S_{\alpha}^{+},S_{\beta}^{-}] = 2\delta_{\alpha\beta}S_{\alpha}^{0} .
\end{equation}
The magnitude of quasi-spin for each level is given by
$S_\alpha=\frac{1}{2}(\Omega_\alpha-\nu_\alpha)$, where $\nu_\alpha$
is the seniority
quantum number, namely the number of unpaired particles at the level $\alpha$.
In the present study, we consider only seniority-zero states with
$\nu=\sum_\alpha \nu_\alpha=0$.
The residual two-body interaction consists of the monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain the exact solutions either by solving the Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasi-spin symmetry.

@@

The time-dependent coherent state for the seniority $\nu=0$ states
($S_\alpha=\Omega_\alpha/2$) is constructed with
time-dependent complex variables $Z_\alpha(t)$ as
\begin{equation}
	\ket{Z(t)} = \prod_{\alpha} \left(1+|Z_\alpha(t)|^2\right)^{-\Omega_\alpha/2}
	\exp [Z_\alpha(t) S_\alpha^{+}] \ket{0},
 \label{coherent}
\end{equation}
where $\ket{0}$ is the vacuum (zero-particle) state.
The TDHFB motion is given by the time development of $Z_\alpha(t)$.
In the SU(2) quasi-spin representation,
$\ket{0}=\prod_\alpha \ket{S_\alpha,-S_\alpha}$.
The coherent state $\ket{Z(t)}$ is a superposition of
the states with different particle numbers
without unpaired particles.
%If $Z_l$ are all real,
In the present pairing model,
the coherent state is the same as the time-dependent BCS wave function
with $Z_\alpha(t)=v_\alpha(t)/u_\alpha(t)$,
where $(u_\alpha(t),v_\alpha(t))$ are the time-dependent BCS $u,v$ factors.

The TDHFB equation can be derived from the time-dependent variational
principle, $\delta \mathcal{S} = 0$, where
\begin{equation}
%  \delta \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
	\mathcal{S}\equiv \int \mathcal{L}(t) dt =
	\int \braket{Z(t)|i\frac{\partial}{\partial t}-H|Z(t)}dt
  \label{TDHFB}
\end{equation}
($\hbar=1$ applies hereafter).
After the transformation of the complex variables into the real ones with
$Z_\alpha = \tan{\frac{\theta_\alpha}{2}}e^{-i\chi_\alpha}$
($0\leq\theta_\alpha\leq\pi$),
the Lagrangian $\mathcal{L}$ and the expectation value of the Hamiltonian
are written as
\begin{equation}
\mathcal{L}(t) = \sum_\alpha \frac{\Omega_\alpha}{2}
	(1-\cos{\theta}_\alpha)\dot{\chi_\alpha} - \mathcal{H}(Z,Z^*) ,
\end{equation}
with
\begin{align}
	\mathcal{H}( &Z,Z^*) \equiv \braket{Z|H|Z}& \nonumber \\
	=& \sum_\alpha \epsilon_\alpha\Omega_\alpha(1- \cos{\theta}_\alpha)
	\nonumber \\
	&- \frac{g}{4}\sum_\alpha \Omega_\alpha [\Omega_\alpha(1-\cos^2{\theta}_\alpha)+(1-\cos{\theta}_\alpha)^2] \nonumber \\
& - \frac{g}{4}\sum_{\alpha\neq \beta} \Omega_{\alpha}\Omega_{\beta} \sqrt{(1-\cos^2{\theta}_{\alpha})(1-\cos^2{\theta}_{\beta})}e^{-i(\chi_{\alpha}-\chi_{\beta})}   .
\label{TDHFB_Hamiltonian_2}
\end{align}
We choose $\chi_\alpha$ as canonical coordinates, and their conjugate momenta
are given by
\begin{align}
  j^\alpha\equiv
	\frac{\partial\mathcal{L}}{\partial\dot{\chi}_\alpha}=\frac{\Omega_\alpha}{2}
	(1-\cos{\theta}_\alpha) .
\end{align}
$\chi_\alpha$ represents a kind of gauge angle of each level,
and $j^\alpha$ corresponds to the occupation number of each level,
$2j^\alpha=\bra{Z} n_\alpha\ket{Z}$. 
As we mention in Sec.~\ref{sec:notation},
we switch the coordinates and momenta,
$(\chi_\alpha,j^\alpha) \rightarrow (j^\alpha,-\chi_\alpha)$,
to make the coordinates time even.
%Therefore, the TDHFB Hamiltonian can be represented by canonical variables
%$\mathcal{H}(Z,Z^*) = \mathcal{H}(\{\chi_l\},\{j_l\})$, and 
The TDHFB equation is equivalent to classical Hamilton's equations
\begin{equation}
	-\dot{\chi_\alpha} = -\frac{\partial\mathcal{H}}{\partial j^\alpha}, \quad
	\dot{j^\alpha} = \frac{\partial\mathcal{H}}{\partial (-\chi_\alpha)} .
\end{equation}

@@

After deriving the collective subspace $\Sigma_2$, 
we perform the quantization according to the SPA in Sec.~\ref{sec:SPA}.
Calculating a trajectory in the $(q^1,p_1)$ space,
we can identify a series of states $\{\ket{\Phi,J;q^1(t),p_1(t)}\}$
on the trajectory,
in the form of Eq. (\ref{coherent})
with parameters $Z_\alpha$ given at $(\Phi,J,q^1,p_1)$ and $q^a=p_a=0$ for
$a\geq 3$.
%Due to $J$ is conserved quantity, the action integral can be divided into two terms
Since the variables $(\Phi,J)$ and $(q^1,p_1)$ are separable,
we may take closed trajectories independently in $(\Phi,J)$ and $(q^1,p_1)$
sectors, which we denote here as $C_\Phi$ and $C_1$, respectively.
The action integral is given by
\begin{align}
\mathcal{T}(\Phi,J;q^1,p_1)
&= \int_{C_\Phi} \braket{\Phi(t),J;q^1,p_1|i\frac{\partial}{\partial t}|\Phi(t),J;q^1,p_1} dt \nonumber \\
+ \int_{C_1} &\braket{\Phi,J;q^1(t),p_1(t)|i\frac{\partial}{\partial t}|\Phi,J;q^1(t),p_1(t)} dt
 \nonumber \\
	&=J\Phi + \int_{C_1} \sum_\alpha j^\alpha d\chi_\alpha
	\nonumber \\
	&\equiv \mathcal{T}_\Phi(J,\Phi) +\mathcal{T}_1(q^1,p_1;J) .
%	\label{tau}
\end{align}
In fact, the gauge-angle dependence is formally given as
\begin{equation}
  \ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_1},
\end{equation}
where $\hat{N}=\sum_\alpha n_\alpha$.
Then, the action for the trajectory $C_1$ can be also expressed as
$\mathcal{T}(q^1,p_1;J)=
 \int_{C_1} \braket{J;q^1,p_1|i\frac{\partial}{\partial t}|J;q^1,p_1} dt$.
%\begin{align}
%  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
%\end{align}
%%where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
%The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.

@@

The calculated wave functions for the excited $0^+$ states 
are shown in Fig. \ref{fig:N16_occ}. 
We show the occupation probabilities which are decomposed 
into the $2n$-particle-$2n$-hole components. 
The left end of the horizontal axis at $m_2-m_1=-8$ $(j=-4)$
corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
are in the lower level $\alpha=1$.
The next one at $m_2-m_1=-6$ $(j=-3)$ corresponds to the one with
$(m_1,m_2)=((N-2)/2,1)$, and so on.
The results from the TDHFB2+SPA and the ASCC+SPA are identical to each other
within numerical error, and they reproduce
the TDHFB+SPA calculation well.
{\bf (How about exact cal.?)}

@@

\subsection{Non-integrable case (1): Three-level pairing model}
\label{sec:three-level-model}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
 \end{center}
	\caption{Pairing gap as a function of collective coordinate $q^1$
	in ${}^{192}$Pb. 
}
 \label{192Pb_gap}
\end{figure}

>>>>

For multi-level pairing models in Sec.~\ref{sec3}, 
there is a constant of motion in the TDHFB dynamics,
namely the average particle number $q^n\equiv \langle \hat{N} \rangle/2$.
Since the particle number $\hat{N}$ is time-even Hermitian operator, we treat
this as a coordinate, and its conjugate gauge angle, $p_n$,
as a momentum.
Since $q^n$ is a constant of motion, the Hamiltonian does not
depend on $p_n$.
On the other hand, the gauge angle $p_n$ changes in time,
which corresponds to the pair rotation, a Nambu-Goldstone (NG) mode
associated with the breaking of the gauge (particle-number) symmetry.
We assume the existence of 2D collective subspace $\Sigma_2$
(4D phase space),
described by a set of canonical variable $(q^1,q^2=q^n;p_1,p_2=p_n)$,
which is well decoupled from the rest of degrees of freedom,
$\{q^a,p_a\}$ with $a=3,\cdots$.
The collective Hamiltonian is given by imposing $q^a=p_a=0$,
namely by restricting the space into the collective subspace
\begin{equation}
%\mathcal{H}_{\rm coll}(q,p) &= \bar{V}(q) + \frac{1}{2}\bar{B}^{-1}(q)p^2 .
\mathcal{H}_{\rm coll}(q,p;q^n)
= \bar{V}(q^1,q^n) + \frac{1}{2}\bar{B}^{11}(q^1,q^n)p_1^2 .
  \label{coll}
\end{equation}
Since there exist two conserved quantities, $q^n$ and $\mathcal{H}_{\rm coll}$,
this 2D system is integrable.
We can treat the collective motion of $(q^1,p_1)$ separately from
the pair rotation $(q^n, p_n)$.

In the collective Hamiltonian (\ref{coll}), the variable $q^n$ is
trivially given as the particle number, which is expanded up to
second order in the momenta $\pi$,
\begin{equation}
q^n=\frac{\langle \hat{N} \rangle}{2} = f^n(\xi)
	+\frac{1}{2}f^{(1)n\alpha\beta}\pi_\alpha\pi_\beta .
	\label{q^n}
\end{equation}
To obtain the non-trivial collective variables
$(q^1,p_1)$, we assume the point transformation\footnote{
We may lift the restriction to the point transformation,
as Eq. (\ref{q^n}) \cite{Sat18}.
In this paper, we neglect these higher-order terms, such as
$f^{(1)1\alpha\beta}\pi_\alpha\pi_\beta/2$.
},
\begin{equation}
%  q = q^1 &= f^1(\xi) + \frac{1}{2}f^{(1)1\alpha\beta}(\xi)\pi_{\alpha}\pi_{\beta}  \label{point}\\
  q^1 = f^1(\xi) \label{point} ,
% \xi^{\alpha} &= g^{\alpha}(q) + \frac{1}{2}g^{(1)\alpha 1 1}(\xi)p_{1}p_{1}
\end{equation}
and $\xi^\alpha$ on the subspace $\Sigma_2$ is given as
$\xi^{\alpha} = g^{\alpha}(q^1,q^n,q^a=0)$.
The momenta on $\Sigma_2$ are transformed as
\begin{align}
p_1 &= g_{,1}^{\alpha}\pi_{\alpha} , \quad p_n = g_{,n}^\alpha \pi_\alpha,
	\label{coll_momenta}\\
\pi_{\alpha} &= f^1_{,\alpha}p_1 +f^n_{,\alpha}p_n,
 \label{momenta}
\end{align}
where the comma indicates the partial derivative
$(f^1_{,\alpha}=\partial f^1/\partial \xi^{\alpha})$. 
The Einstein's convention for summation with respect to the repeated
upper and lower indices is assumed hereafter.
The canonical variable condition leads to
\begin{align}
 %f^1_{,\alpha}g_{,1}^{\beta} = \delta^{\beta}_{\alpha}, \quad 
f^i_{,\alpha}g_{,j}^{\alpha} = \delta^i_j,
  \label{canonicity}
\end{align}
where $i,j=1$ and $n$.
The collective potential $\bar{V}(q^1,q^n)$ and
the collective mass parameter
$\bar{B}_{11}(q^1,q^n)=[\bar{B}^{11}(q^1,q^n)]^{-1}$ can be given by
\begin{align}
\bar{V}(q^1,q^n) &= V(\xi=g(q^1,q^n,q^a=0)), \\
\bar{B}^{11}(q^1,q^n) &= f^1_{,\alpha}\tilde{B}^{\alpha\beta}(\xi)f^1_{,\beta} ,
  \label{coll_mass}
\end{align}
where $\tilde{B}^{\alpha\beta}$ are defined as
\begin{align}
 \tilde{B}^{\alpha\beta}(\xi)
%&= \frac{\partial^2 \mathcal{H}_M}{\partial\pi_{\alpha}\partial\pi_{\beta}}  \nonumber \\
&= B^{\alpha\beta}(\xi) - \bar{V}_{,n} f^{(1)n\alpha\beta}(\xi)
%- \lambda_1 f^{(1)1\alpha\beta}(\xi) 
\label{tildeB}.
\end{align}

@@

At each point in the space $(q^1,q^n; p_1,p_n)$ corresponds to
a generalized Slater determinant
$\ket{q^1,q^n;p_1,p_n}=\ket{\xi,\pi}$
where $(\xi,\pi)$ are given as
$\xi^\alpha=g^\alpha(q^1,q^n,q^a=0)$ and
$\pi_\alpha=f^1_{,\alpha}p_1+f^n_{,\alpha}p_n$.
According to the SPA, the $k$-th excited state $\ket{\psi_k}$
is constructed from the $k$-th periodic trajectory $C_k$,
given by $(q^1(t),p_1(t))$,
of the Hamiltonian $\mathcal{H}_{\rm coll}$.
\begin{equation}
%\ket{\psi_k} = \oint_{C_k} d\mu(q,p) \ket{q,p}
\ket{\psi_k} \propto \oint dp_n \oint_{C_k} \rho(q,p) dt \ket{q,p}
	e^{i\mathcal{T}[q,p]} ,
	\label{SPA}
\end{equation}
where $(q,p)$ means $(q^1,q^n;p_1, p_n)$, and the weight function
$\rho(q,p)$ is given through an invariant measure $d\mu(q,p)$ as
\begin{equation}
d\mu(q,p)=\rho(q,p) dE dt dq^n dp_n .
\end{equation}
The invariant measure $d\mu(q,p)$ is defined by the unity condition
$\int d\mu(q,p) \ket{q,p}\bra{q,p} = 1$.
An explicit form of $d\mu(q,p)$ for the present pairing model is shown
in Eq. (\ref{dmu}).
The action integral $\mathcal{T}$ is defined by
\begin{align}
\mathcal{T}[q,p] &\equiv
\int_{0}^{t} \braket{q(t'),p(t')| i\frac{\partial}{\partial t'}
	|q(t'),p(t')} dt' .
\label{tau}
\end{align}

@@

We study the low-lying excited $0^+$ states
in the multi-level pairing model by applying the ASCC+SPA.
The Hamiltonian of the pairing model is given in terms of
the single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{align}
	\hat{H} &= \sum_\alpha \epsilon_\alpha \hat{n}_\alpha - g \sum_{\alpha,\beta} \hat{S}_\alpha^+ \hat{S}_{\beta}^- \nonumber \\
    &= \sum_\alpha\epsilon_\alpha(2\hat{S}_\alpha^0+\Omega_\alpha) - g \hat{S}^+ \hat{S}^{-} ,
\end{align}
where we use the SU(2) quasi-spin operators,
$\boldsymbol{S}=\sum_\alpha \boldsymbol{S}_\alpha$, with
\begin{eqnarray}
        \hat{S}_\alpha^0 &=& \frac{1}{2}\left(\sum_m\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha m}-\Omega_\alpha\right) ,\\
        \hat{S}_\alpha^{+} &=& \sum_{m>0}\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha\overline{m}}^{\dag} ,
\quad   \hat{S}_\alpha^{-} = \hat{S}_\alpha^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_\alpha$ possesses $2\Omega_\alpha$-fold
degeneracy ($\Omega_\alpha=j_\alpha+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$
and $\Omega_\alpha-1/2$.
The occupation number of each level $\alpha$ is given by
$\hat{n}_\alpha = \sum_m \hat{a}^{\dag}_{j_\alpha m}\hat{a}_{j_\alpha m}
=2\hat{S}_\alpha^0+\Omega_\alpha
$.
The quasi-spin operators satisfy the commutation relations
\begin{equation}
  [\hat{S}_\alpha^0,\hat{S}_\beta^{\pm}] = \pm\delta_{\alpha\beta}\hat{S}_{\alpha}^{\pm},
\quad [\hat{S}_{\alpha}^{+},\hat{S}_{\beta}^{-}] = 2\delta_{\alpha\beta}\hat{S}_{\alpha}^{0} .
\end{equation}
The magnitude of quasi-spin for each level is given by
$S_\alpha=\frac{1}{2}(\Omega_\alpha-\nu_\alpha)$, where $\nu_\alpha$
is the seniority
quantum number, namely the number of unpaired particles at the level $\alpha$.
In the present study, we consider only seniority-zero states with
$\nu=\sum_\alpha \nu_\alpha=0$.
The residual two-body interaction consists of the monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain the exact solutions either by solving the Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasi-spin symmetry.

@@

The time-dependent coherent state for the seniority $\nu=0$ states
($S_\alpha=\Omega_\alpha/2$) is constructed with
time-dependent complex variables $Z_\alpha(t)$ as
\begin{equation}
	\ket{Z(t)} = \prod_{\alpha} \left(1+|Z_\alpha(t)|^2\right)^{-\Omega_\alpha/2}
	\exp [Z_\alpha(t) \hat{S}_\alpha^{+}] \ket{0},
 \label{coherent}
\end{equation}
where $\ket{0}$ is the vacuum (zero-particle) state.
The TDHFB motion is given by the time development of $Z_\alpha(t)$.
In the SU(2) quasi-spin representation,
$\ket{0}=\prod_\alpha \ket{S_\alpha,-S_\alpha}$.
The coherent state $\ket{Z(t)}$ is a superposition of
the states with different particle numbers
without unpaired particles.
%If $Z_l$ are all real,
In the present pairing model,
the coherent state is the same as the time-dependent BCS wave function
with $Z_\alpha(t)=v_\alpha(t)/u_\alpha(t)$,
where $(u_\alpha(t),v_\alpha(t))$ are the time-dependent BCS $u,v$ factors.

The TDHFB equation can be derived from the time-dependent variational
principle, $\delta \mathcal{S} = 0$, where
\begin{equation}
%  \delta \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
	\mathcal{S}\equiv \int \mathcal{L}(t) dt =
	\int \braket{Z(t)|i\frac{\partial}{\partial t}-\hat{H}|Z(t)}dt
  \label{TDHFB}
\end{equation}
($\hbar=1$ applies hereafter).
After the transformation of the complex variables into the real ones with
$Z_\alpha = \tan{\frac{\theta_\alpha}{2}}e^{-i\chi_\alpha}$
($0\leq\theta_\alpha\leq\pi$),
the Lagrangian $\mathcal{L}$ and the expectation value of the Hamiltonian
are written as
\begin{equation}
\mathcal{L}(t) = \sum_\alpha \frac{\Omega_\alpha}{2}
	(1-\cos{\theta}_\alpha)\dot{\chi}_\alpha - \mathcal{H}(Z,Z^*) ,
\end{equation}
with
\begin{align}
	\mathcal{H}( &Z,Z^*) \equiv \braket{Z|\hat{H}|Z}& \nonumber \\
	=& \sum_\alpha \epsilon_\alpha\Omega_\alpha(1- \cos{\theta}_\alpha)
	\nonumber \\
	&- \frac{g}{4}\sum_\alpha \Omega_\alpha [\Omega_\alpha(1-\cos^2{\theta}_\alpha)+(1-\cos{\theta}_\alpha)^2] \nonumber \\
& - \frac{g}{4}\sum_{\alpha\neq \beta} \Omega_{\alpha}\Omega_{\beta} \sqrt{(1-\cos^2{\theta}_{\alpha})(1-\cos^2{\theta}_{\beta})}e^{-i(\chi_{\alpha}-\chi_{\beta})}   .
\label{TDHFB_Hamiltonian_2}
\end{align}
We choose $\chi_\alpha$ as canonical coordinates, and their conjugate momenta
are given by
\begin{align}
  j^\alpha\equiv
	\frac{\partial\mathcal{L}}{\partial\dot{\chi}_\alpha}=\frac{\Omega_\alpha}{2}
	(1-\cos{\theta}_\alpha) .
\end{align}
$\chi_\alpha$ represents a kind of gauge angle of each level,
and $j^\alpha$ corresponds to the occupation number of each level,
$2j^\alpha=\bra{Z} \hat{n}_\alpha\ket{Z}$. 
As we mention in Sec.~\ref{sec:notation},
we switch the coordinates and momenta,
$(\chi_\alpha,j^\alpha) \rightarrow (j^\alpha,-\chi_\alpha)$,
to make the coordinates time even.
%Therefore, the TDHFB Hamiltonian can be represented by canonical variables
%$\mathcal{H}(Z,Z^*) = \mathcal{H}(\{\chi_l\},\{j_l\})$, and 
The TDHFB equation is equivalent to classical Hamilton's equations
\begin{equation}
	-\dot{\chi}_\alpha = -\frac{\partial\mathcal{H}}{\partial j^\alpha}, \quad
	\dot{j}^\alpha = \frac{\partial\mathcal{H}}{\partial (-\chi_\alpha)} .
\end{equation}

@@

After deriving the collective subspace $\Sigma_2$, 
we perform the quantization according to the SPA in Sec.~\ref{sec:SPA}.
Calculating a trajectory in the $(q^1,p_1)$ space,
we can identify a series of states $\{\ket{\Phi,J;q^1(t),p_1(t)}\}$
on the trajectory,
in the form of Eq. (\ref{coherent})
with parameters $Z_\alpha$ given at $(\Phi,J,q^1,p_1)$ and $q^a=p_a=0$ for
$a\geq 3$.
%Due to $J$ is conserved quantity, the action integral can be divided into two terms
Since the variables $(\Phi,J)$ and $(q^1,p_1)$ are separable,
we may take closed trajectories independently in $(\Phi,J)$ and $(q^1,p_1)$
sectors, which we denote here as $C_\Phi$ and $C_1$, respectively.
The action integral is given by
\begin{align}
\mathcal{T}(\Phi,J;q^1,p_1)
&= \int_{C_\Phi} \braket{\Phi(t),J;q^1,p_1|i\frac{\partial}{\partial t}|\Phi(t),J;q^1,p_1} dt \nonumber \\
+ \int_{C_1} &\braket{\Phi,J;q^1(t),p_1(t)|i\frac{\partial}{\partial t}|\Phi,J;q^1(t),p_1(t)} dt
 \nonumber \\
	&=J\Phi + \int_{C_1} \sum_\alpha j^\alpha d\chi_\alpha
	\nonumber \\
	&\equiv \mathcal{T}_\Phi(J,\Phi) +\mathcal{T}_1(q^1,p_1;J) .
%	\label{tau}
\end{align}
In fact, the gauge-angle dependence is formally given as
\begin{equation}
  \ket{\Phi,J;q^1,p_1} = e^{-i\Phi \hat{N}/2} \ket{J;q^1,p_1},
\end{equation}
where $\hat{N}=\sum_\alpha \hat{n}_\alpha$.
Then, the action for the trajectory $C_1$ can be also expressed as
$\mathcal{T}(q^1,p_1;J)=
 \int_{C_1} \braket{J;q^1,p_1|i\frac{\partial}{\partial t}|J;q^1,p_1} dt$.
%\begin{align}
%  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
%\end{align}
%%where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
%The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.

@@

The calculated wave functions for the excited $0^+$ states 
are shown in Fig. \ref{fig:N16_occ}. 
We show the occupation probabilities which are decomposed 
into the $2n$-particle-$2n$-hole components. 
The left end of the horizontal axis at $m_2-m_1=-8$ $(j=-4)$
corresponds to a state with $(m_1,m_2)=(N/2,0)$ where all the particles
are in the lower level $\alpha=1$.
The next one at $m_2-m_1=-6$ $(j=-3)$ corresponds to the one with
$(m_1,m_2)=((N-2)/2,1)$, and so on.
The results from the TDHFB2+SPA and the ASCC+SPA are identical to each other
within numerical error, and they reproduce
the TDHFB+SPA calculation well.

@@

\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{omega_sq.eps}
 \end{center}
 \caption{Eigenvalues of moving-frame QRPA equation as a function of
the collective coordinate $q^1$, from $N=14$ to $N=24$.
The thick (green) lines are the modes we choose as
the collective coordinate $q^1$,
while the dashed lines correspond to the zero modes ($q^n$).
In each panel, both ends of the horizontal axis corresponds
to the ending points of the collective path $q^1$.
}
 \label{omega_sq}
\end{figure*}
\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{occ_number.eps}
 \end{center}
\caption{Occupation numbers in each single-particle level
as a function of the collective coordinate $q^1$,
from $N=14$ to $N=24$.
The purple, green, and blue lines correspond to
$\alpha=1$, 2, and 3, respectively.
At the left end point of the collective coordinate in each panel,
the configurations correspond to the ``HF-like'' states.
See text for details.
}
 \label{occ_number}
\end{figure*}
\subsection{Non-integrable case (1): Three-level pairing model}
\label{sec:three-level-model}

@@
